Digital History in Finland, 1488-1828

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

Title counts in selected places.

Ja lisäksi sitten muu kuin Suomi tai Ruotsi julkaisumaana.

@@

>>>>

Title counts in selected places in the Kungliga catalogue.

@@

Kungliga publications outside Sweden and Finland.

```{r selectedplaces2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="0px"}

  # Use timeinterval year intervals
  catal = "Kungliga"
  minyear = 1500
  #maxyear = 1800
  #minyear = min(na.omit(df0$publication_year))
  #maxyear = max(na.omit(df0$publication_year))

  df = subset(df0, !country %in% c("Finland", "Sweden") & catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year < maxyear)

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot(data = dfm, aes(x = date, y = Documents))
  p <- p + geom_line(col = "black")
  p <- p + geom_smooth(col = "black")  
  p <- p + geom_point(col = "black", size = 3)
  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste("Outside of Sweden and Finland", " (", catal, ")", sep = ""))
  print(p)

```
